---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramarital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.

```{r}
source("makeTables2016.R")
```


# Sex

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Looking at the following bar chart, we can determine how wrong people consider extramarital sex according to their sex. In this graph, the views are split into three categories: 1 - "wrong" in which extramarital sex is considered always or almost always wrong, 2- "Hmmm" in which extramarital sex is considered sometimes wrong, and 3 - "OK" in which extramarital sex is considered to be not wrong at all. 
```{r}
barchartGC(xsex_sex,type="percent")
```
  
    
From this barchart, it appears that there is a relationship between sex and view of extramarital sex. The women are more likely to consider extramarital sex wrong than men (~55% women versus ~45% men). Directly proportional to these view, women are **less** likely to consider extramarital sex ok than men (~45% women versus ~55% men). The percentage of men and women who view extramarital sex as only wrong sometimes appears to be more evenly split, with 51% being men and 49% being women. Overall, men and women have opposing views.  
    
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
rowPerc(xsex_sex)
colPerc(xsex_sex)
```

The data shown above reveals that women are more likely to believe that extramarital sex is wrong than men. Out of those who said extramarital sex is wrong, 56.89% were women and 43.11% were men. In the other two opinion categories that consider extramarital sex either ok or wrong some of the time, men accounted for the majority of votes at 54.9% and 51.55% respectively. Looking at the `colPerc` function, we see that within the male group and female group, the majority of people consider extramarital sex to be wrong.

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
Next, we will perform a Chi-square test to determine if our results apply to the population at large. We will state our null and alternative hypotheses.  

$H_0$: Being a male or female is independent of one's view on extramarital sex.  
$H_a$: One's view on extramarital sex is dependent on being male or female.  

```{r}
chisqtestGC(xsex_sex, graph=TRUE)
```

According to the chi-square test, our p-value is 0.0351. This means that if the null hypothesis is correct, we should expect to see these same results about 3 percent of the time. With this low p-value under our standard of 0.05, we must reject the null hypothesis. Instead, we conclude that it is likely that one's sex has an influence on their view of extramarital sex.  

# Political Views

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

# Relationship Status

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
